A quantitative framework for investigating the reliability of empirical network construction: supplemental information

### 2019-01-16 manuscript/reply_to_reviewers.tex

		Our mention of habitat as a factor affecting the probability of species interacting at a site was not intended to refer to species using different habitats, but rather the possibility that habitat type might affect interaction probabilities. For example, a more open patch of forest might have different interaction probabilities than a denser patch even if the same set of species use both patches. The Reviewer is clearly correct that habitat also affects which species are present at a site. We included co-occurrence in process uncertainty since co-occurrence does not tell us much about whether an interaction is feasible under ideal conditions (which would certainly include co-occurrence). This speaks to our point above that external factors (habitat, weather, etc.) can affect multiple levels of uncertainty at once. In fact, habitat also likely affects detection uncertainty since it is often harder to observe interactions in dense vegetation. So, in short, separating sources of uncertainty based on the external factors which contribute to them is not a particularly useful endeavour and we have revised the manuscript to steer readers away from it.

@@

	7. Point about temporal scales of interaction [[done]]

		\begin{refquote}
		L76ff Different interactions occur at different temporal scales, so it is important to consider where the role of this study lies. For instance, a pollinator-flower interaction is quick (and even the evidence of it, e.g. pollen on the insect, is not long-lasting) whereas an active gall-former interaction could be present for a couple of months and could be detected for even longer (on senescing leaves).
		\end{refquote}

		\textbf{R:} Long-term interactions may be easier to detect, but this does not necessarily translate into reduced process uncertainty. Spatial variation in interaction probabilities will affect all interaction types, as does variation in abundances between years, so we cannot conceive of any interactions that are exempt from this issue. The timescale of an interaction (and the evidence it leaves) does affect detection uncertainty, so we have added a note in that section (lines 137-140). Long-term interactions may still fail to be detected, however, and we now add an example to make it clear that detection uncertainty applies to even long-term interactions such as gall-forming (indeed, our results suggest that uncertainty in gall-forming is quite high).

		Perhaps more important is the effect of sampling interval. As sampling time increases toward infinity, interaction probabilities should converge to 0 or 1 with no uncertainty. As we discuss, however, sampling times are limited by resources, the trade-off between sampling a single site intensively versus many sites, etc. Any interaction could therefore occur outside of the sampling window and hence be missed.

		Lines 137-140:

		\begin{quotation}
			The probability of detecting an interaction will also depend on the duration of the interaction and its evidence, the species involved, and the individuals sampled~\citep{Wells2013,Lagrue2015,Cirtwill2016,Weinstein2017}. 
		\end{quotation}

	8. Confusion about goal of modelling

		\begin{refquote}
		I was struggling to really understand what the authors were really trying to model (partly because of the lack of a link between the theoretical and empirical parts of the paper). Are the authors trying to estimate L (the probability that an interaction is feasible or not – I would describe this as a `master' or meta- network), or is it that they are trying to estimate X|L (the probability that the interaction locally occurs)? I would be interested in both, but the second aspect seemed to be ignored in the gall-former example.
		\end{refquote}

		\textbf{R:} In the case study, we are modelling L (the probability that an interaction is feasible). We do not have quantitative data within sites in our dataset, so we cannot isolate the probability of detecting an interaction at a site from the probability that the interaction occurs. This is also the probability we were most interested in. We do note, however, that one could also model X|L using the same framework if there were independent counts of co-occurrences and interactions within a single site. [[Add ref to the 2018 paper that does this]] does just this. We now state throughout the manuscript that we are interested in compiling the metaweb, the set of interaction which can feasibly occur. We hope that our goal is now crystal clear.

	9. Misunderstanding of how biased sampling does not solve problems of uncertainty

@@

		\begin{refquote}
		L136 This is a completely different issue, that you do not address in the paper.
		\end{refquote}

		\textbf{R:} We do not believe that biased sampling is a completely different issue as the tendency for some interactions to be sampled more easily than others clearly contributes to varying levels of detection uncertainty. Increasing sampling effort will not do much good if we repeatedly sample the same common interactions and very rarely identify any new interactions. We now address questions about whether or not sampling more will remove uncertainty in a dedicated appendix (\emph{Appendix S2}). We still mention the fact that increased sampling will not reduce uncertainty evenly across interactions as this is an important point to consider when designing sampling protocols and when analysing empirical data. We also point out that combining sampling types is a partial solution to this problem; if different sampling methods have different biases, they may partially cancel each other out. We believe that this addresses the question as much as possible given our focus on analysing collected data rather than collecting new data.

	10. Explain Bayesian approach more simply

@@

	11. Integrate L155ff with previous section

		\begin{refquote}
		L155ff I think it would be helpful for this section to be integrated with the previous section. It relies on the reader putting quite a lot of work in to understand the link between the two.
		\end{refquote}

		\textbf{R:} We have removed much of the introductory text explaining which quantity we are most interested in ($\lambda$) and now more explicitly state our goals at the end of the introduction. We hope that the transition to the methods is now less work for a reader.

	12. Ideas presented in L209, L262, L310 are important but explained too briefly

@@

		\begin{refquote}
		L209ff This seems a really important set of ideas, but they are exemplified very briefly and very simplistically in the paper (L262, L310). I would have appreciated a much clearer explanation and example.
		\end{refquote}

		\textbf{R:} We are not quite sure what the Reviewer is asking here. $\alpha$ and $\beta$ truly are quite simple (as simple as the mean and standard deviation of a normal distribution) so there is not much more to say about them in themselves. We have expanded our discussion of different types of priors and how they may be obtained, and we hope that this clarifies matters for the Reviewer. We also note that a simple worked example, with accompanying R code, is provided in \emph{Appendix S4} so that readers can see exactly how to obtain $\alpha$ and $\beta$. In case the point of confusion is the idea that $\alpha$ and $\beta$ can be specified or derived depending on the type of prior desired, we have added a line (lines 181-185) spelling this out.

		\begin{quotation}
			The shape parameters, or hyperparameters, may be set to particular values or derived from some data (see below). They may be set to the same values for all interactions, allowed to vary independently for all interactions, or incorporate non-independence between interactions (e.g., when the shape of the prior distribution depends upon species' abundances or traits). 
			\end{quotation}

	13. Reframe line 241 in terms of solutions rather than difficulties

		\begin{refquote}
		L241 I wonder if you could phrase this more positively as `solutions' rather than just `difficulties'?
		\end{refquote}

		\textbf{R:} We appreciate the Reviewer's desire for optimism, but we also selected a high-quality dataset specifically in order to demonstrate that empirically sampling all of the feasible interactions in a system is very unlikely. A lower-quality dataset would work just as well with our framework but would not highlight these difficulties so well. We have therefore kept this line as-is but have expanded the paragraph (301-307) to show how the Bayesian framework provides a partial solution to the problems inherent in even high-quality empirical data.

		\begin{quotation}
		 The high spatiotemporal resolution of this dataset makes it ideal for illustrating the difficulties in completely sampling a network; even with such an unusually high sampling effort, there were many pairs of species which were rarely or never observed together and about which we therefore have high uncertainty about interaction probabilities (Fig. 2). Using the Bayesian framework above, we can identify which potential interactions are more and less uncertain, allowing us to better predict the true structure of the metaweb. 
		 \end{quotation}

	14. Line 283 seems to be a very important point and should be explained more clearly

@@

		\textbf{R:} Due to space constraints, we have refrained from adding an extensive description of Jensen's inequality here, but are confident that readers can find a fuller description in the online literature if they choose.

	15. Line 291: does assuming probability of 1 for observed interactions introduce bias? [[done]]

		\begin{refquote}
		L291 I have wondered about this – does assuming a probability of 1 for observed interactions create a bias? The observed interactions are a stochastic set of the possible interactions, so by treating observed interactions as 1 and other (equally likely?) unobserved interactions as \textless1 will surely bias the network metrics. I'm not sure of the solution and would welcome thoughts on this in the paper.
		\end{refquote}

		\textbf{R:} As we are concerned with the metaweb (the set of feasible interactions) rather than the interactions which occur at a given site on a given day, we do not think that assuming a probability of 1 for observed interactions introduces bias in our study. We have added a justification of setting the probability of observed interactions to 1 in \emph{Appendix S3}. Note that each posterior web is a prediction of the true metaweb and not a local realisation of some interactions drawn from the feasible set. These local webs are more akin to our ``filtered webs'' in which observed interactions are not guaranteed to appear.

		One interesting point is whether systems with a large risk of false positives (e.g., pollination networks which assume all flower visitors provide pollination service) would be biased by assuming all observed interactions are truly feasible. Assuming that all interactions which are known to be feasible actually occur at each site would also introduce bias - I suspect that this is what the Reviewer may be thinking of. As described above, our study cannot isolate $\chi$ (the probability that a feasible interaction occurs at a particular site), so this is not a relevant question for the present work. Future studies with much, much more detailed data may be able to shed light on this.

		We suspect, however, that the Reviewer may be thinking of weighted networks where interaction frequencies of feasible (occurring somewhere in the metaweb) interactions vary. In this case, the probability of an interaction will almost never be 1 as an interaction which occurred 10 times in 10 observed co-occurrences might not occur at an 11th observation. As discussed above, this is an interesting avenue for future extensions but beyond the scope of the present manuscript.

	16. Filtering seems arbitrary

@@

		\begin{refquote}
		L298 These seem arbitrary. It is not clear what is filtered, or its justification – is it the unique interactions, unique interaction per site or samples? How do these compare to typical sampling effort?
		\end{refquote}

		\textbf{R:} We have rephrased our description (in \emph{Appendix S10}) to make it clearer that the filtered networks are intended to demonstrate how network structure changes as uncertainty increases (and we miss more interactions). As stated, we filtered networks created using the posterior distributions. There are therefore no sites or samples in question here. We are simply retaining a random 90\%-10\% of the interactions (or removing a random 10\%-90\%; these are equivalent) of the interactions in the ``true'' (posterior) network. We hope that this rephrasing is clearer.

			\begin{quotation}
				Measures of network structure which are based on empirical networks that are missing interactions may differ substantially from the values that would be obtained if detection certainty and variation in interactions over space and time could be removed. To demonstrate this, we created a suite of filtered networks for each posterior network. Taking a posterior network as the ``true'' network, we randomly sampled 90\%, 80\%, 70\%, 60\%, 50\%, 40\%, 30\%, 20\%, and 10\% of the interactions to create a new ``filtered'' network.
			\end{quotation}

		Note that our model is not concerned with partitioning different sources of variation; the filtering levels we present therefore represent uncertainty from all sources. As such, comparing them directly to ``typical sampling effort'' would be an apples-to-oranges comparison. We do note that~\citet{Weinstein2017a} found a detectability of 23.3\% for interactions despite high sampling effort,~\citet{Jordano2016} found that about half of unobserved interactions did not qualify as ``forbidden links``, and~\citet{Bartomeus2013} found that 59\% of interactions were detected. We therefore do not think that the range of filtering levels we applied were particularly unreasonable (although we note that none of the above studies refer to plant-galler networks). That said, the Reviewer is correct that the values we chose were absolutely arbitrary. To make this clear, we now filter in 10\% increments from 90\% to 10\% to illustrate a broader range of uncertainty.

	17. Expand discussion of results on line 321

@@

		\begin{refquote}
		L321 This is a really important and interesting set of results that are worthy of greater discussion. The issue of metrics from sampled networks is important, but gets lost in the paper. Please expand upon this.
		\end{refquote}

		\textbf{R:} Ultimately, length restrictions meant that we were obliged to remove our discussion of network metrics to an appendix (\emph{Appendix S10}). After adding the additional material requested by Reviewers in the methods, there simply was not space to discuss the network-level metrics in the main manuscript. We agree with the Reviewer that this is an extremely important question, but feel that it is essential to provide a clear and useable explanation of the basic Bayesian framework in the present manuscript. We hope to return to the question of how network metrics are impacted by sampling issues in more detail in future work.
